---
title: "RMarkdown Demo"
author: "Avi Kluger"
date: "January 30, 2019"
output:
  word_document: default
  html_document: default
---

# Method
## Participants

But with HTML you can also write

<center> <h1>Method</h1> </center>
## Participants

```{r}
load("ListeningFinal.RData")
```
## Participants

```{r echo=FALSE}
load("ListeningFinal.RData")
```
A total of `r nrow(l_scale_df)` answered the listening survey, M~age~ = `r round(mean(l_scale_df$age_1, na.rm = TRUE), 1)`, `r round((mean(l_scale_df$gender, na.rm = TRUE) - 1) *100, 1)`% females.

Descritive statistics is provided in Table 1.

```{r echo=FALSE}
if (!require('psych')) install.packages('psych'); library('psych')

startColumn <- grep("trust", names(l_scale_df))
endColumn   <- ncol(l_scale_df)

describe(l_scale_df[, startColumn:endColumn])
describe(l_scale_df[, startColumn:endColumn])[, c("mean", "sd", "skew", "kurtosis")]

library('knitr')
Table1 <- describe(l_scale_df[, startColumn:endColumn])[, c("mean", "sd", "skew", "kurtosis")]
kable(Table1)
```

But, we also provide the rounded results

```{r, echo=FALSE}
kable(round(Table1, 2), caption = "Descriptive statistics for listening-related scales")
```

Surprisingly, we did not find the interaction we did not hypothesized.  As can be seen in Figure 1.

```{r echo=FALSE, message=FALSE}
if (!require('pequod')) install.packages('pequod'); library('pequod')
mod <- lmres(support ~ PAIR*tenure, center = c("PAIR", "tenure"), 
             data = l_scale_df)
S_slopes <- simpleSlope(mod, pred = "PAIR", mod1 = "tenure")
PlotSlope(S_slopes)
```




