---
title: "Feedback IDC"
author: "Avi Kluger"
date: "February 1, 2019"
output: html_document
---

```{r echo=FALSE}

# Drop test rows and Qualtrics columns and the first Text message
df      <- df [, -c(1:10)]
df      <- df [-c(1:21), -5]


```

# R workshop feedback

At the end of the workshop, I asked you to answer four questions:

1. Overall, I am satisfied with the content of the R workshop
2. Overall, I am satisfied with the content of the lecturer
3. Please write comments
4. if a summer workshop with Avi Kluger will be offered on using R for HLM, SEM, and advanced topics, will you register?

Below is the code, explained, and the resulting analyses.

I read the data from Qualtrics, not shown here.  I dropped one line with missing values.  I was left with 20 valid responses.  I created an empty data frame that has names that could include spaces, and replaced the names of the df with the names I created in temp_df.

Next, I loaded the *psych* library and produced just the very basic statistics for the first two items


```{r}
df <- na.omit(df)

temp_df <- data.frame("Course Satisfaction" = numeric(), 
                      "Lecturer Satisfaction" = numeric(),
                      "Comments" = character(),
                      "Interest in future workshops" = numeric(), 
                      check.names = FALSE)

names(df) <- names(temp_df)

library(psych)

describe(df[, 1:2]) [c("n", "mean", "sd")]
```

Next, I tested whether you were more satisfied with the lecturer than with the course, using paired-sample *t*-test.

```{r}
t.test(df$`Course Satisfaction`, 
       df$`Lecturer Satisfaction`, 
       paired=TRUE, 
       conf.level=0.95)
```

The results of *t*-test indicated that you were more satisfied with the lecturer than with the course.  Next, I choose the comments that were not empty AND not in Hebrew (the 4th and the 5th answer)

```{r}
Comments <- df$Comments[which(df$Comments != "")][-c(4:5)]
library(knitr)
kable(Comments[-1], caption = "Comments regarding the R workshop",
      col.names = c("verbatim"))
```


Finally, I converted the `Interest in future workshops` into a factor, and defined labels for its levels, and I used barplot to show the frequencies of your responses.

```{r}
df$`Interest in future workshops` <- factor(df$`Interest in future workshops`,
                                        levels = (c(0, 0.5, 1)),
                                        labels = c("Not interested",
                                                   "Perhaps",
                                                   "Interested"))
barplot(table(df$`Interest in future workshops`), main = 
   "Frequencies of levels of interest in future R workshop\nwith Avi Kluger")
```


