---
title: "RMarkdown Demo"
author: "Avi Kluger"
date: "January 30, 2019"
output:
  word_document: default
  html_document: default
---
#Method
##Participants

```{r echo=FALSE}
load("ListeningFinal.RData")
```
A total of `r nrow(l_scale_df)` answered the listening survey, *M*~age~ = `r round(mean(l_scale_df$age_1, na.rm = TRUE), 1)` (`r round(sd(l_scale_df$age_1, na.rm = TRUE), 2)`), `r round((mean(l_scale_df$gender, na.rm = TRUE) - 1) *100, 1)`% females.

Descritive statistics is provided in Table 1.

```{r echo=FALSE, message=FALSE}
if (!require('psych')) install.packages('psych'); library('psych')

startColumn <- grep("trust", names(l_scale_df))
endColumn   <- ncol(l_scale_df)

library('knitr')
Table1 <- describe(l_scale_df[, startColumn:endColumn])[, c("mean", "sd", "skew", "kurtosis")]

kable(round(Table1, 2), 
      caption = "Table 1. Descriptive statistics for listening-related scales")
```

Surprisingly, we did not find the interaction we did not hypothesized.  As can be seen in Figure 1.

```{r echo=FALSE, message=FALSE}
if (!require('pequod')) install.packages('pequod'); library('pequod')
mod <- lmres(support ~ PAIR*tenure, center = c("PAIR", "tenure"), 
             data = l_scale_df)
S_slopes <- simpleSlope(mod, pred = "PAIR", mod1 = "tenure")
theme_set(theme_bw())
PlotSlope(S_slopes)
```

*Figure 1.* The effect of learning too much R in one week on the well-being of novices by tenure in using SPSS or Stata


